---
title: "Lab 7 Fernanda"
author: "Fernanda Montero"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hi this is Fernanda 
How is it going
it going chill

if your collaboraor: 

load the tidyverse
read in the kermit data as 'kermit'
make some side-by-side histograms of the Score.pre for all respondents, separated by the gender column

```{r}
library(tidyverse)

kermit <- read_csv("kermit.csv")

kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender)

kermit_hist
```

Creator: Preform rank-based comparisons using Mann-Whitney U and Wilcoxon-Signed Rank

Question: is there a significant difference in pre-talk ranks of Kermit for Male and Female respondents?

```{r}
mwu_kermit <- kermit %>% 
  wilcox.test(Score.pre ~ Gender,data = .)

#Null hypothesis: There is NOT a significant difference in ranks for male and female respondents

#Alternative: There IS a significant difference in ranks

mwu_kermit


```

There was no significant difference in ranks for male and female respondents (W=155.5, p=0.4, alpha = 0.05)""

